

---
title: "RMarkDownLeaflet"
author: "Manoj"
date: "December 12, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
Leaflet is one of the most popular Javascript libraries for creating interactive maps. The leaflet R package allows you to create your own leaflet maps without needing to know any Javascript!


#Installation

```
install.packages("leaflet")
```


#Display My Map

```
library(leaflet)
my_map <- leaflet() %>% 
  addTiles()
my_map


```

```{r out.width='100%', echo=FALSE}
library(leaflet)
my_map <- leaflet() %>%
  addTiles()
my_map
```

## Manoj Office

```
my_map <- my_map %>%
  addMarkers(lat=12.937014, lng=77.607508, 
             popup="Manoj Office")
my_map

```

```{r out.width='100%', echo=FALSE}
my_map <- my_map %>%
  addMarkers(lat=12.937014, lng=77.607508, 
             popup="Manoj Office")
my_map
```




#Adding Markers

```

set.seed(2018-11-12)
df <- data.frame(lat = runif(20, min = 12.8, max = 12.9),
                 lng = runif(20, min = 77.5, max = 77.6))
df %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers()

```


```{r out.width='100%', echo=FALSE}

set.seed(2018-11-12)
df <- data.frame(lat = runif(20, min = 12.8, max = 12.9),
                 lng = runif(20, min = 77.5, max = 77.6))
df %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers()

```


#Adding Many Markers

```

  
  accentureIcon <- makeIcon(
  iconUrl = "https://www.accenture.com/t20180820T081710Z__w__/us-en/_acnmedia/Accenture/Dev/Redesign/Acc_Logo_Black_Purple_RGB.PNG",
  iconWidth = 40*215/230, iconHeight = 35,
  iconAnchorX = 40*215/230/2, iconAnchorY = 20
)

accentureLatLong <- data.frame(
  lat = c(12.29, 12.32, 12.29),
  lng = c(77.59, 77.62, 77.54))

accentureLatLong %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(icon = accentureIcon)
  
  
```


```{r out.width='100%', echo=FALSE}


  
  accentureIcon <- makeIcon(
  iconUrl = "https://www.accenture.com/t20180820T081710Z__w__/us-en/_acnmedia/Accenture/Dev/Redesign/Acc_Logo_Black_Purple_RGB.PNG",
  iconWidth = 40*215/230, iconHeight = 35,
  iconAnchorX = 40*215/230/2, iconAnchorY = 20
)

accentureLatLong <- data.frame(
  lat = c(12.29, 12.32, 12.29),
  lng = c(77.59, 77.62, 77.54))

accentureLatLong %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(icon = accentureIcon)

```


#Different sites
```
accentureSite <- c(
  "<a href='http://www.accenture.com/'>BDC3</a>",
  "<a href='http://www.accenture.com/'>BDC9</a>",
  "<a href='http://www.accenture.com/'>BDC4</a>"
  
  )

accentureLatLong %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(icon = accentureIcon, popup = accentureSite)
  
  
 
```
```{r out.width='100%', echo=FALSE}
accentureSite <- c(
  "<a href='http://www.accenture.com/'>BDC3</a>",
  "<a href='http://www.accenture.com/'>BDC9</a>",
  "<a href='http://www.accenture.com/'>BDC4</a>"
  
  )

accentureLatLong %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(icon = accentureIcon, popup = accentureSite)
  
  
 
```


#Making Custom Markers
```
df <- data.frame(lat = runif(500, min = 12.25, max = 12.35),
                 lng = runif(500, min = -76.65, max = -76.55))
df %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(clusterOptions = markerClusterOptions())
  

```
```{r out.width='100%', echo=FALSE}
df <- data.frame(lat = runif(500, min = 12.25, max = 12.35),
                 lng = runif(500, min = -76.65, max = -76.55))
df %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(clusterOptions = markerClusterOptions())
  

```


#Adding circles
```
md_cities <- data.frame(name = c("Bangalore", "BTM", "JPNagar", "JayaNagar", 
                                 "Madiwala", "Jakkasandra", "Majestic", "Silkboard", "Whitefield", "HosurRoad"),
                        pop = c(619493, 66169, 62334, 61045, 55232,
                                39890, 38880, 30587, 30484, 25346),
                        lat = c(12.2920592, 12.4143921, 12.0840, 12.1434, 12.0068, 12.6418, 12.9784, 13.9897, 14.3607, 15.0993),
                        lng = c(76.6077852, 77.4204875, 77.1528, 77.2014, 76.7791, 77.7200, 76.4922, 76.9378, 75.5994, 76.8483))
md_cities %>%
  leaflet() %>%
  addTiles() %>%
  addCircles(weight = 1, radius = sqrt(md_cities$pop) * 30)
  

```

```{r out.width='100%', echo=FALSE}
md_cities <- data.frame(name = c("Bangalore", "BTM", "JPNagar", "JayaNagar", 
                                 "Madiwala", "Jakkasandra", "Majestic", "Silkboard", "Whitefield", "HosurRoad"),
                        pop = c(619493, 66169, 62334, 61045, 55232,
                                39890, 38880, 30587, 30484, 25346),
                        lat = c(12.2920592, 12.4143921, 12.0840, 12.1434, 12.0068, 12.6418, 12.9784, 13.9897, 14.3607, 15.0993),
                        lng = c(76.6077852, 77.4204875, 77.1528, 77.2014, 76.7791, 77.7200, 76.4922, 76.9378, 75.5994, 76.8483))
md_cities %>%
  leaflet() %>%
  addTiles() %>%
  addCircles(weight = 1, radius = sqrt(md_cities$pop) * 30)
  

```


#Adding rectangle 

```
leaflet() %>%
  addTiles() %>%
  addRectangles(lat1 = 12.3858, lng1 = 77.0595, 
                lat2 = 12.3890, lng2 = 77.0625)

```
```{r out.width='100%', echo=FALSE}
leaflet() %>%
  addTiles() %>%
  addRectangles(lat1 = 12.3858, lng1 = 77.0595, 
                lat2 = 12.3890, lng2 = 77.0625)
```



#Adding Legends
```
df <- data.frame(lat = runif(20, min = 12.25, max = 12.35),
                 lng = runif(20, min = 76.65, max = 77.55),
                 col = sample(c("red", "blue", "green"), 20, replace = TRUE),
                 stringsAsFactors = FALSE)

df %>%
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers(color = df$col) %>%
  addLegend(labels = LETTERS[1:3], colors = c("blue", "red", "green"))
```

```{r out.width='100%', echo=FALSE}
df <- data.frame(lat = runif(20, min = 12.25, max = 12.35),
                 lng = runif(20, min = 76.65, max = 77.55),
                 col = sample(c("red", "blue", "green"), 20, replace = TRUE),
                 stringsAsFactors = FALSE)

df %>%
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers(color = df$col) %>%
  addLegend(labels = LETTERS[1:3], colors = c("blue", "red", "green"))
```
